---
title: "Data"
author: "masri"
date: "2023-08-06"
output: html_document
---

A code chunk only for libraries.
```{r}
unique_dataset <- final_dataset %>% 
  select(country, var) %>% 
  distinct()

# Print the unique dataset
print(unique_dataset)
names(final_dataset)
```

```{r}
# Load the required library
library(dplyr)

# Your existing dataset is assumed to be 'merged_data' and your newly created dataset is 'filtered_data'

# Create a mapping dataframe for country abbreviations and full names
country_mapping <- data.frame(
  country = c("JOR", "IRQ", "TUN", "MOR", "EGY", "LEB", "LIB"),
  countryname = c("Jordan", "Iraq", "Tunisia", "Morocco", "Egypt, Arab Rep.", "Lebanon", "Libya")
)

# Merge the mapping dataframe with the existing dataset to get full country names
merged_data_with_fullnames <- left_join(merged_data, country_mapping, by = "country")

# Merge to add the 'var' column from filtered_data
final_dataset <- left_join(merged_data_with_fullnames, filtered_data[, c("countryname", "var")], by = "countryname")

# Optionally, remove the 'countryname' column after the merging
final_dataset$countryname <- NULL

```


```{r}
# Load dplyr package
library(dplyr)

# Original dataset is wgidataset

# Create a data frame containing the target countries and years
target_data <- data.frame(
  countryname = c("Egypt, Arab Rep.", "Iraq", "Jordan", "Lebanon", "Libya", "Morocco", "Tunisia"),
  year = c(2016, 2016, 2016, 2016, 2017, 2016, 2016)
)

# Merge the original dataset (wgidataset) with target_data on 'countryname' and 'year'
filtered_data <- wgidataset %>%
  inner_join(target_data, by = c("countryname", "year")) %>%
  select(countryname, year, var)  # select only the columns we need

# View the filtered data
print(filtered_data)


```

# List of specific countries

Take only specific columns after we extracted only the desired countries. 7 Wave
```{r}

# List of desired countries
desired_countries <- c("JOR", "IRQ", "TUN", "MOR", "EGY", "LEB", "LIB")

# Filter the dataset to include only the desired countries
Wave_7_selected <- subset(Wave_7, C_COW_ALPHA %in% desired_countries, select = c("C_COW_ALPHA", "Q46",
                                                                "Q47", "Q48", "Q49",
                                             "Q50", "Q57", "Q209", "Q210", "Q211", "Q212",
                                             "Q213",
                                             "Q215", "Q218", "Q219", "Q220", "Q173",
                                             "Q262", "Q260", "Q279"))

```

Take only specific columns after we extracted only the desired countries. 6 Wave
```{r}
# List of desired countries
desired_countries <- c("JOR", "IRQ", "TUN", "MOR", "EGY", "LEB", "LBY")

# Filter the dataset to include only the desired countries
Wave_6_selected <- subset(Wave_6, C_COW_ALPHA %in% desired_countries, select = c("C_COW_ALPHA", "V10", "V11", "V55", "V23",
                                             "V59", "V24", "V85", "V86", "V87", "V88",
                                             "V147","V242", "V240", "V229"))

```

naming the attributes with meaningful names. 7 Wave
```{r}
library(dplyr)
Wave_7_renamed <- Wave_7_selected %>%
   rename(happiness = Q46, free_choice = Q48, health = Q47, life_satis = Q49,
          financial_satis = Q50, gen_trust = Q57,
          sign_pet = Q209, join_boycott = Q210,
          attend_demo = Q211, join_strike = Q212, donate = Q213, enc_poli = Q215, 
          sign_pet_onli = Q218, enc_poli_onli = Q219, org_poli_onli = Q220,
          religiosity = Q173, age = Q262, gender = Q260, employment = Q279 , 
          country = C_COW_ALPHA)
          
```

naming the attributes with meaningful names. 6 Wave
```{r}
library(dplyr)
Wave_6_renamed <- Wave_6_selected %>%
   rename(happiness = V10, health = V11, free_choice = V55, life_satis = V23, 
          financial_satis = V59, gen_trust = V24, sign_pet = V85, join_boycott = V86,
          attend_demo = V87,
          join_strike = V88, religiosity = V147, age = V242, gender = V240,
          employment = V229, country = C_COW_ALPHA)
          
```

cleaning the dataset. 7 Wave
```{r}
for (col in names(Wave_7_renamed)) {
  Wave_7_renamed[[col]][Wave_7_renamed[[col]] %in% 
  c(-1, -2, -4, -5)] <- NA
}

```

cleaning the dataset. 6 Wave
```{r}
for (col in names(Wave_6_renamed)) {
  Wave_6_renamed[[col]][Wave_6_renamed[[col]] %in% 
  c(-1, -2, -4, -5)] <- NA
}
```

merge the two data sets.
```{r}
# Load required libraries
library(dplyr)

# Create a mapping to align country codes
country_mapping <- data.frame(original_country = c('LIB'), mapped_country = c('LBY'))

# Apply the mapping to Wave_6_renamed dataset
Wave_6_renamed <- Wave_6_renamed %>%
  left_join(country_mapping, by = c("country" = "original_country")) %>%
  mutate(country = coalesce(mapped_country, country)) %>%
  select(-mapped_country)

# Merge the datasets (Wave_6_renamed and Wave_7_renamed)
merged_data <- bind_rows(Wave_6_renamed, Wave_7_renamed)

# Remove unwanted columns
merged_data <- merged_data[, !(names(merged_data) %in% c("org_poli_onli", "enc_poli_onli", "sign_pet_onli", "donate", "enc_poli"))]
unique(merged_data$country)

```

visualize the missing values for every attibute in the merged data.
```{r}
library(ggplot2)

# Assuming 'merged_data' is your data frame
missing_proportions <- colMeans(is.na(merged_data))
missing_data_df <- data.frame(variable = names(missing_proportions), proportion = missing_proportions)

# Create a bar chart to visualize missing data proportions
ggplot(missing_data_df, aes(x = variable, y = proportion)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  labs(title = "Proportion of Missing Data by Variable", x = "Variable", y = "Proportion Missing") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

specifying the location of the missing values within the attributes in the merged data.
``` {r}
library(naniar)
library(ggplot2)

# Function to summarize and visualize missing data for each country
missing_summary_and_visualization_by_country <- function(merged_data) {
  country <- unique(merged_data$country)[1]
  missing_summary <- sapply(merged_data, function(x) sum(is.na(x)))
  print(paste("Missing data summary for", country, ":"))
  print(missing_summary)
  
  plot <- naniar::vis_miss(merged_data) + 
    ggtitle(paste("Missing Data Visualization for", country)) +
    theme_minimal() +
    theme(plot.margin = margin(t = 0.5, r = 0.5, b = 2, l = 0.5, unit = "cm"),
          axis.text.x = element_text(angle = 90, hjust = 1))  # Adjust angle and bottom margin
  
  print(plot)
}

# Apply the function to each subset of the data, grouped by country
by(merged_data, merged_data$country, missing_summary_and_visualization_by_country)

```

calculating and printing the propotions of the missing data in the merged data.
```{r}
library(dplyr)
library(writexl)

# Your existing code for summarizing missing proportions
merged_data %>%
  group_by(country) %>%
  summarise(across(
    .cols = everything(),
    .fns = ~ mean(is.na(.x)),
    .names = "{.col}_missing_proportion"
  )) -> missing_proportions

# Specify the file path where you want to save the Excel file
output_path <- "C:/Users/LENOVO/Desktop/DataMohammed/Data/missing_proportion.xlsx"

# Save the summarized data to an Excel file
write_xlsx(missing_proportions, path = output_path)

cat("Excel file saved at:", output_path, "\n")
```

visualize the missing data according to the attributes in merged data using dlookr library.
```{r}
library(dlookr)
plot_na_pareto(merged_data)
plot_na_intersect(merged_data)
```

a heat map for the miising data in the merged data.
```{r}
library(naniar)
gg_miss_fct(x = merged_data, fct = country)
```

creating a data frame to do iterations and imputation then do the missForest imputation method to handle the missing data.
```{r}
library(missRanger)
library(ggplot2)

merged_data_na <- data.frame(final_dataset)

merged_imputet <- missRanger(
  merged_data_na, 
  formula = . ~ . ,
  num.trees = 1000, 
  verbose = 2, 
  seed = 111,  
  returnOOB = T)
```

calculating and printing the propotions of the missing data in the merged data after the imputation.
```{r}
library(dplyr)
library(tidyr)
merged_imputet_rounded %>%
  group_by(country) %>%
  summarise(across(
    .cols = everything(),
    .fns = ~ mean(is.na(.x)),
    .names = "{.col}_missing_proportion"
  )) -> missing_proportions_imputed

# Print the result
print(missing_proportions_imputed)
```

comparison between the imputed and the original data for *all attributes* by bar chart. *imputed in red*.
```{r}
library(ggplot2)
library(scales)

# Create the plot
data_columns <- setdiff(names(merged_data), c("country", "age", "gender"))

# Create a list to store plots
plots <- list()

# Generate bar charts for each column
for (col in data_columns) {
  unique_values <- unique(merged_data[[col]])
  plot <- ggplot() +
    geom_bar(data = merged_data, aes(x = factor(.data[[col]])), width = 0.3) +
    geom_bar(data = merged_imputet_rounded, aes(x = factor(.data[[col]])), fill = "red",
             position = position_nudge(x = 0.25), width = 0.3) +
    scale_x_discrete(breaks = unique_values, labels = numeric_labels[match(unique_values, merged_data[[col]])]) +
    labs(title = paste("Bar Chart for", col)) +
    theme_minimal()
  
  plots[[col]] <- plot
}

# Specify the file path where you want to save the PDF file
output_path <- "C:/Users/LENOVO/Desktop/DataMohammed/Data/plots.pdf"

# Create a PDF device
pdf(output_path)

# Print or display the generated plots and save them in the PDF
for (col in data_columns) {
  print(plots[[col]])
}

# Close the PDF device
dev.off()

cat("PDF file saved at:", output_path, "\n")

```


comparison between the imputed and the original data for *religiosity* by bar chart. *imputed in red*.
```{r}
library(ggplot2)
library(scales)

# Define the string labels and their corresponding numeric values
numeric_labels <- c("1" = "Several times a day", "2"  = "Once a day",
                    "3" = "Several times each week",
                    "4" = "Only when attending religious services",
                    "5" = "Only on special holy days", "6" = "Once a year",
                    "7" = "Less often", "8" = "Never, practically never",
                    "null" = "null")

# Create the plot
ggplot() +
  geom_bar(data = merged_data, aes(x = factor(religiosity)), width = 0.3) +
  geom_bar(data = merged_imputet_rounded, aes(x = factor(religiosity)), fill = "red",
           position = position_nudge(x = 0.25), width = 0.3) +
  scale_x_discrete(breaks = unique(merged_data$religiosity), 
                   labels = numeric_labels) +  # Apply labels
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate and adjust

```

comparison between the imputed and the original data for *happiness* by bar chart. *imputed in red*.
```{r}
library(ggplot2)
library(scales)

# Define the string labels and their corresponding numeric values
numeric_labels <- c("1" = "Very happy", "2"  = "Quite happy", "3" = "Not very happy",
                    "4" = "Not at all happy", "null" = "null")

# Create the plot
ggplot() +
  geom_bar(data = merged_data, aes(x = factor(happiness)), width = 0.3) +
  geom_bar(data = merged_imputet_rounded, aes(x = factor(happiness)), fill = "red",
           position = position_nudge(x = 0.25), width = 0.3) +
  scale_x_discrete(breaks = unique(merged_data$happiness), 
                   labels = numeric_labels) +  # Apply labels
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate and adjust

```

comparison between the imputed and the original data for *free_choice* by bar chart. *imputed in red*.
```{r}
library(ggplot2)
library(scales)

# Define the string labels and their corresponding numeric values
numeric_labels <- c("1" = "None at all", "2" = "2", "3" = "3", "4" = "4", "5" = "5",
                    "6" = "6", "7" = "7", "8" = "8", "9" = "9",
                    "10" = "A great deal", "null" = "null ")

# Create the plot
ggplot() +
  geom_bar(data = merged_data, aes(x = factor(free_choice)), width = 0.3) +
  geom_bar(data = merged_imputet_rounded, aes(x = factor(free_choice)), fill = "red",
           position = position_nudge(x = 0.25), width = 0.3) +
  scale_x_discrete(breaks = unique(merged_data$free_choice), 
                   labels = numeric_labels) +  # Apply labels
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate and adjust

```

comparison between the imputed and the original data for *health* by bar chart. *imputed in red*.
```{r}
library(ggplot2)
library(scales)

# Define the string labels and their corresponding numeric values
numeric_labels <- c("1" = "Very good", "2" = "Good", "3" = "Fair",
                    "4" = "Poor", "null" = "null ")

# Create the plot
data_columns <- setdiff(names(merged_data), c("country", "age", "gender"))
ggplot() +
  geom_bar(data = merged_data, aes(x = factor(health)), width = 0.3) +
  geom_bar(data = merged_imputet_rounded, aes(x = factor(health)), fill = "red",
           position = position_nudge(x = 0.25), width = 0.3) +
  scale_x_discrete(breaks = unique(merged_data$health), 
                   labels = numeric_labels) +  # Apply labels
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate and adjust

```

comparison between the imputed and the original data for *life_satis* by bar chart. *imputed in red*.
```{r}
library(ggplot2)
library(scales)

# Define the string labels and their corresponding numeric values
numeric_labels <- c("1" = "Completely dissatisfied", "2" = "2", "3" = "3",
                    "4" = "4", "5" = "5", "6" = "6", "7" = "7", "8" = "8",
                    "9" = "9","10" = "Completely satisfied", "null" = "null")

# Create the plot
data_columns <- setdiff(names(merged_data), c("country", "age", "gender"))
ggplot() +
  geom_bar(data = merged_data, aes(x = factor(life_satis)), width = 0.3) +
  geom_bar(data = merged_imputet_rounded, aes(x = factor(life_satis)), fill = "red",
           position = position_nudge(x = 0.25), width = 0.3) +
  scale_x_discrete(breaks = unique(merged_data$life_satis), 
                   labels = numeric_labels) +  # Apply labels
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate and adjust

```

comparison between the imputed and the original data for *financial_satis* by bar chart. *imputed in red*.
```{r}
library(ggplot2)
library(scales)

# Define the string labels and their corresponding numeric values
numeric_labels <- c("1" = "dissatisfied", "2" = "2", "3" = "3",
                    "4" = "4", "5" = "5", "6" = "6", "7" = "7", "8" = "8",
                    "9" = "9","10" = "satisfied", "null" = "null")

# Create the plot
data_columns <- setdiff(names(merged_data), c("country", "age", "gender"))
ggplot() +
  geom_bar(data = merged_data, aes(x = factor(financial_satis)), width = 0.3) +
  geom_bar(data = merged_imputet_rounded, aes(x = factor(financial_satis)), fill = "red",
           position = position_nudge(x = 0.25), width = 0.3) +
  scale_x_discrete(breaks = unique(merged_data$financial_satis), 
                   labels = numeric_labels) +  # Apply labels
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate and adjust

```

comparison between the imputed and the original data for *gen_trust* by bar chart. *imputed in red*.
```{r}
library(ggplot2)
library(scales)

# Define the string labels and their corresponding numeric values
numeric_labels <- c("1" = "Most people can be trusted", "2" = "Need to be very careful",
                    "null" = "null ")

# Create the plot
data_columns <- setdiff(names(merged_data), c("country", "age", "gender"))
ggplot() +
  geom_bar(data = merged_data, aes(x = factor(gen_trust)), width = 0.3) +
  geom_bar(data = merged_imputet_rounded, aes(x = factor(gen_trust)), fill = "red",
           position = position_nudge(x = 0.25), width = 0.3) +
  scale_x_discrete(breaks = unique(merged_data$gen_trust), 
                   labels = numeric_labels) +  # Apply labels
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate and adjust

```

comparison between the imputed and the original data for *sign_pet* by bar chart. *imputed in red*.
```{r}
library(ggplot2)
library(scales)

# Define the string labels and their corresponding numeric values
numeric_labels <- c("1" = "Have done", "2" = "Might do",
                    "3" = "Would never do", "null" = "null ")

# Create the plot
data_columns <- setdiff(names(merged_data), c("country", "age", "gender"))
ggplot() +
  geom_bar(data = merged_data, aes(x = factor(sign_pet)), width = 0.3) +
  geom_bar(data = merged_imputet_rounded, aes(x = factor(sign_pet)), fill = "red",
           position = position_nudge(x = 0.25), width = 0.3) +
  scale_x_discrete(breaks = unique(merged_data$sign_pet), 
                   labels = numeric_labels) +  # Apply labels
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate and adjust

```

comparison between the imputed and the original data for *join_boycott* by bar chart. *imputed in red*.
```{r}
library(ggplot2)
library(scales)

# Define the string labels and their corresponding numeric values
numeric_labels <- c("1" = "Have done", "2" = "Might do",
                    "3" = "Would never do", "null" = "null ")

# Create the plot
data_columns <- setdiff(names(merged_data), c("country", "age", "gender"))
ggplot() +
  geom_bar(data = merged_data, aes(x = factor(join_boycott)), width = 0.3) +
  geom_bar(data = merged_imputet_rounded, aes(x = factor(join_boycott)), fill = "red",
           position = position_nudge(x = 0.25), width = 0.3) +
  scale_x_discrete(breaks = unique(merged_data$join_boycott), 
                   labels = numeric_labels) +  # Apply labels
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate and adjust

```

comparison between the imputed and the original data for *attend_demo* by bar chart. *imputed in red*.
```{r}
library(ggplot2)
library(scales)

# Define the string labels and their corresponding numeric values
numeric_labels <- c("1" = "Have done", "2" = "Might do",
                    "3" = "Would never do", "null" = "null ")

# Create the plot
data_columns <- setdiff(names(merged_data), c("country", "age", "gender"))
ggplot() +
  geom_bar(data = merged_data, aes(x = factor(attend_demo)), width = 0.3) +
  geom_bar(data = merged_imputet_rounded, aes(x = factor(attend_demo)), fill = "red",
           position = position_nudge(x = 0.25), width = 0.3) +
  scale_x_discrete(breaks = unique(merged_data$attend_demo), 
                   labels = numeric_labels) +  # Apply labels
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate and adjust

```

comparison between the imputed and the original data for *join_strike* by bar chart. *imputed in red*.
```{r}
library(ggplot2)
library(scales)

# Define the string labels and their corresponding numeric values
numeric_labels <- c("1" = "Have done", "2" = "Might do",
                    "3" = "Would never do", "null" = "null ")

# Create the plot
data_columns <- setdiff(names(merged_data), c("country", "age", "gender"))
ggplot() +
  geom_bar(data = merged_data, aes(x = factor(join_strike)), width = 0.3) +
  geom_bar(data = merged_imputet_rounded, aes(x = factor(join_strike)), fill = "red",
           position = position_nudge(x = 0.25), width = 0.3) +
  scale_x_discrete(breaks = unique(merged_data$join_strike), 
                   labels = numeric_labels) +  # Apply labels
  theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate and adjust

```

comparison between the imputed and the original data for *employment* by bar chart. *imputed in red*.
```{r}
library(ggplot2)
library(scales)

# Define the string labels and their corresponding numeric values
numeric_labels <- c("1" = "Full time", "2" = "Part time", "3" = "Self employed",
                    "4" = "Retired", "5" = "Housewife not otherwise employed",
                    "6" = "Student", "7" = "Unemployed", "null" = "null")

# Create the plot
data_columns <- setdiff(names(merged_data), c("country", "age", "gender"))
ggplot() +
  geom_bar(data = merged_data, aes(x = factor(employment)), width = 0.3) +
  geom_bar(data = merged_imputet_rounded, aes(x = factor(employment)), fill = "red",
           position = position_nudge(x = 0.25), width = 0.3) +
  scale_x_discrete(breaks = unique(merged_data$employment), 
                   labels = numeric_labels) +  # Apply labels
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate and adjust

```

renaming the data in the data set.
```{r}
#=======employment==========================================================================
employment_mapping <- c(
  "1" = "Full time",
  "2" = "Part time",
  "3" = "Self employed",
  "4" = "Retired",
  "5" = "Housewife not otherwise employed",
  "6" = "Student",
  "7" = "Unemployed",
  "null" = "null"
)
#=======join_strike=========================================================================

join_strike_mapping <- c(
  "1" = "Have done",
  "2" = "Might do",
  "3" = "Would never do",
  "null" = "null"
)
#=======attend_demo=========================================================================

attend_demo_mapping <- c(
  "1" = "Have done",
  "2" = "Might do",
  "3" = "Would never do",
  "null" = "null"
)
#=======join_boycott========================================================================

join_boycott_mapping <- c(
  "1" = "Have done",
  "2" = "Might do",
  "3" = "Would never do",
  "null" = "null"
)
#=======sign_pet============================================================================

sign_pet_mapping <- c(
  "1" = "Have done",
  "2" = "Might do",
  "3" = "Would never do",
  "null" = "null"
)
#=======gen_trust===========================================================================

gen_trust_mapping <- c(
  "1" = "Most people can be trusted",
  "2" = "Need to be very careful",
  "null" = "null"
)
#=======financial_satis=====================================================================

financial_satis_mapping <- c(
  "1" = "Dissatisfied",
  "2" = "2",
  "3" = "3",
  "4" = "4",
  "5" = "5",
  "6" = "6",
  "7" = "7",
  "8" = "8",
  "9" = "9",
  "10" = "Satisfied",
  "null" = "null"
)
#=======life_satis==========================================================================

life_satis_mapping <- c(
  "1" = "compeltely dissatisfied",
  "2" = "2",
  "3" = "3",
  "4" = "4",
  "5" = "5",
  "6" = "6",
  "7" = "7",
  "8" = "8",
  "9" = "9",
  "10" = "compeltely Satisfied",
  "null" = "null"
)
#=======health============================================================================

health_mapping <- c(
  "1" = "Very good",
  "2" = "Good",
  "3" = "Fair",
  "4" = "Poor",
  "null" = "null"
)
#=======free_choice=========================================================================

free_choice_mapping <- c(
  "1" = "None at all",
  "2" = "2",
  "3" = "3",
  "4" = "4",
  "5" = "5",
  "6" = "6",
  "7" = "7",
  "8" = "8",
  "9" = "9",
  "10" = "A great deal",
  "null" = "null"
)
#=======happiness===========================================================================

happiness_mapping <- c(
  "1" = "Very happy",
  "2" = "Quite happy",
  "3" = "Not very happy",
  "4" = "Not at all happy",
  "null" = "null"
)
#=======gender===========================================================================

gender_mapping <- c(
  "1" = "Male",
  "2" = "Female",
  "null" = "null"
)

#=======religiosity=========================================================================

religiosity_mapping <- c(
  "1" = "Several times a day",
  "2"  = "Once a day",
  "3" = "Several times each week",
  "4" = "Only when attending religious services",
  "5" = "Only on special holy days",
  "6" = "Once a year",
  "7" = "Less often",
  "8" = "Never, practically never",
  "null" = "null"
)

#=======adding changes to new data frame====================================================

merged_renamed <- merged_imputet_rounded %>%
  mutate(
    employment = employment_mapping[as.character(employment)],
    join_strike = join_strike_mapping[as.character(join_strike)],
    attend_demo = attend_demo_mapping[as.character(attend_demo)],
    join_boycott = join_boycott_mapping[as.character(join_boycott)],
    sign_pet = sign_pet_mapping[as.character(sign_pet)],
    gen_trust = gen_trust_mapping[as.character(gen_trust)],
    financial_satis = financial_satis_mapping[as.character(financial_satis)],
    life_satis = life_satis_mapping[as.character(life_satis)],
    health = health_mapping[as.character(health)],
    free_choice = free_choice_mapping[as.character(free_choice)],
    happiness = happiness_mapping[as.character(happiness)],
    gender = gender_mapping[as.character(gender)],
    religiosity = religiosity_mapping[as.character(religiosity)]
  )
# Print the new dataframe
print(merged_renamed)
```

calculating the descriptive statistics for the whole data.
```{r}
library(dplyr)
library(writexl)

# Create a function to calculate descriptive statistics
calculate_descriptive_stats <- function(data, variable_name) {
  data %>%
    group_by(country) %>%
    summarise(
      variable_name = variable_name,
      mean = mean(.data[[variable_name]], na.rm = TRUE),
      median = median(.data[[variable_name]], na.rm = TRUE),
      mode = as.numeric(names(sort(table(.data[[variable_name]]), decreasing = TRUE)[1])),
      variance = var(.data[[variable_name]], na.rm = TRUE),
      standard_deviation = sd(.data[[variable_name]], na.rm = TRUE),
      range = paste(range(.data[[variable_name]], na.rm = TRUE), collapse = " - "),
      iqr = IQR(.data[[variable_name]], na.rm = TRUE),
      skewness = skewness(.data[[variable_name]], na.rm = TRUE),
      kurtosis = kurtosis(.data[[variable_name]], na.rm = TRUE)
    )
}

# Create an empty data frame to store the results
results_df <- data.frame()

# List of variables to include
variables <- c(
  "happiness", "gen_trust", "health", "free_choice", "life_satis",
  "financial_satis", "gen_trust", "sign_pet", "join_boycott", "attend_demo",
  "join_strike", "religiosity", "gender", "employment"
)

# Loop through variables and calculate descriptive stats
for (variable in variables) {
  descriptive_stats <- calculate_descriptive_stats(merged_data, variable)
  results_df <- bind_rows(results_df, descriptive_stats)
}

# Save results to an Excel file (replace "descriptive_stats.xlsx" with your preferred filename)
write_xlsx(results_df, "descriptive_stats.xlsx")

```

calculating the descriptive data for each country and put it in a list of data frames.
```{r}
# Load required libraries
library(e1071)
library(dplyr)
library(openxlsx)

# Function to calculate variable summaries by country and save in separate sheets
descriptive_summary <- function(data, variables, output_file) {
  # Initialize a new Excel workbook
  wb <- createWorkbook()
  
  for (country_name in unique(data$country)) {
    country_data <- data %>%
      filter(country == country_name)
    
    country_summary <- country_data %>%
      summarize(across(all_of(variables), .names = "mean_{.col}", mean, na.rm = TRUE),
                across(all_of(variables), .names = "median_{.col}", median, na.rm = TRUE),
                across(all_of(variables), .names = "mode_{.col}", ~as.numeric(names(sort(table(.x), decreasing = TRUE)[1]))),
                across(all_of(variables), .names = "variance_{.col}", var, na.rm = TRUE),
                across(all_of(variables), .names = "sd_{.col}", sd, na.rm = TRUE),
                across(all_of(variables), .names = "range_{.col}", ~paste(range(.x, na.rm = TRUE), collapse = " - ")),
                across(all_of(variables), .names = "iqr_{.col}", IQR, na.rm = TRUE),
                across(all_of(variables), .names = "skewness_{.col}", skewness, na.rm = TRUE),
                across(all_of(variables), .names = "kurtosis_{.col}", kurtosis, na.rm = TRUE))
    
    # Create a new sheet with the country name
    addWorksheet(wb, sheetName = country_name)
    
    # Write the summary data to the sheet
    writeData(wb, sheet = country_name, x = country_summary)
  }
  
  # Save the workbook to the specified output file
  saveWorkbook(wb, file = output_file)
  
  cat("Summary data has been saved to the following Excel file:\n")
  cat(output_file)
}

# Define the file path for the Excel file
file_path <- "C:/Users/LENOVO/Desktop/DataMohammed/Data/country_variable_summaries.xlsx"

# List of variables for summaries
variables <- c("happiness", "gen_trust", "health", "free_choice",
               "life_satis", "financial_satis", "gen_trust",
               "sign_pet", "join_boycott", "attend_demo",
               "join_strike", "religiosity", 
               "age", "gender", "employment") 

# Generate the summaries and save in separate sheets
descriptive_summary(merged_data, variables, output_file = file_path)

```

calculate the values separately and visualize it.
```{r}
# Load required libraries
library(dplyr)
library(moments)
library(ggplot2)

# Assuming your dataset is named "your_dataset"
# Replace "your_dataset" with the actual name of your dataset

country_data <- merged_imputet_rounded %>%
  filter(country == "EGY")  # Filter data for EGY country

# List of variable names to calculate statistics for
variable_names <- c("happiness", "gen_trust", "health", "free_choice",
                    "life_satis", "financial_satis", "gen_trust",
                    "sign_pet", "join_boycott", "attend_demo",
                    "join_strike", "religiosity", 
                    "age", "gender", "employment")

# Initialize an empty list to store results
results_list <- list()

# Loop through each variable and calculate statistics
for (variable_name in variable_names) {
  variable_stats <- country_data %>%
    summarise(
      variable_name = variable_name,
      mean = mean(!!sym(variable_name), na.rm = TRUE),
      median = median(!!sym(variable_name), na.rm = TRUE),
      mode = as.numeric(names(sort(table(!!sym(variable_name)), decreasing = TRUE)[1])),
      variance = var(!!sym(variable_name), na.rm = TRUE),
      standard_deviation = sd(!!sym(variable_name), na.rm = TRUE),
      range = paste(range(!!sym(variable_name), na.rm = TRUE), collapse = " - "),
      iqr = IQR(!!sym(variable_name), na.rm = TRUE),
      skewness = skewness(!!sym(variable_name), na.rm = TRUE),
      kurtosis = kurtosis(!!sym(variable_name), na.rm = TRUE)
    )
  
  results_list[[variable_name]] <- variable_stats
}

# Combine results into a single data frame
results_df <- bind_rows(results_list)

# Print the results
print(results_df)


# List of variables to exclude
excluded_variables <- c("age", "gender")

# Filter out the excluded variables from the dataframe
filtered_results <- results_df %>% filter(!variable_name %in% excluded_variables)

# Create a bar chart for mean values
mean_bar_chart <- ggplot(filtered_results, aes(x = variable_name, y = mean)) +
  geom_bar(stat = "identity", fill = "blue") +
  labs(title = "Mean Values for Different Variables (Excluding Age and Gender) in EGY Country",
       x = "Variable", y = "Mean Value") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Print the bar chart
print(mean_bar_chart)

library(writexl)

# Define the file path for the Excel file
file_path <- "C:/Users/LENOVO/Desktop/DataMohammed/Data/statistics_results.xlsx"

# Write the data frame to the specified Excel file path
write_xlsx(filtered_results, path = file_path)



```

multilevel analysis
```{r}
# Load necessary packages
library(lme4)
library(tidyverse)
model1 <- lmer(sign_pet ~ happiness + health + free_choice + life_satis + financial_satis + 
               gen_trust + age + gender + employment + religiosity + 
               (1|country) + var, data = final_dataset)
```


```{r}
model1_adv <- lmer(sign_pet ~ happiness * var + health + free_choice + life_satis + financial_satis + 
                   gen_trust + age * gender + employment + religiosity + 
                   (1 + happiness + age|country), 
                   data = final_dataset)
summary(model1_adv)

```


```{r}
# Load the required packages
library(lme4)
library(lmerTest)

# Load the dataset

# Fit the multivariate multilevel model
model <- lmer(cbind(sign_pet, join_boycott, attend_demo, join_strike) ~ 
              happiness + health + free_choice + life_satis + financial_satis +
              gen_trust + age + gender + employment + religiosity + 
              (1 + happiness + health + free_choice + life_satis + financial_satis | country) +
              (1 | var), 
              data = final_dataset)

# Show the model summary
summary(model)

# Produce various diagnostic plots
plot(model)
```


```{r}
fit1 <- lmer(sign_pet ~ happiness + health + free_choice + life_satis + financial_satis + (1 | country/var), data = final_dataset)
summary(fit1)

```


```{r}
# Load the required packages
library(lme4)
library(lmerTest)

# Load your dataset
# final_dataset <- read.csv("path/to/your/dataset.csv")

# Fit the multivariate multilevel models
fit1 <- lmer(sign_pet ~ happiness + health + free_choice + life_satis + financial_satis + (1 + happiness + health | country/var), data = final_dataset)
fit2 <- lmer(join_boycott ~ happiness + health + free_choice + life_satis + financial_satis + (1 + happiness + health | country/var), data = final_dataset)
fit3 <- lmer(attend_demo ~ happiness + health + free_choice + life_satis + financial_satis + (1 + happiness + health | country/var), data = final_dataset)
fit4 <- lmer(join_strike ~ happiness + health + free_choice + life_satis + financial_satis + (1 + happiness + health | country/var), data = final_dataset)

# Summarize the results
summary(fit1)
summary(fit2)
summary(fit3)
summary(fit4)

```
