---
title: "Data"
author: "masri"
date: "2023-08-06"
output: html_document
---

A code chunk only for libraries.
```{r}
rm(merged_data_new, merged_data_vis, merged_data_vis_2, merged_imputet_1, missing_proportions_new, Wave_6_new, Wave_6_selected_new, Wave_6_try, Wave_7_new, Wave_7_renamed_new, Wave_7_selected_new, Wave_7_try)
```

taking only the 7 desired countries from the original dataset. 7 Wave
```{r}
desired_countries <- c("JOR", "IRQ", "TUN", "MOR", "EGY", "LBN", "LIB")

# Filter the data for specific countries
Wave_7 <- `WVS_Cross-National_Wave_7_v5_0`[`WVS_Cross-National_Wave_7_v5_0`$C_COW_ALPHA %in% desired_countries, ]

```

taking only the 7 desired countries from the original dataset. 6 Wave
```{r}
desired_countries <- c("JOR", "IRQ", "TUN", "MOR", "EGY", "LEB", "LBY")

# Filter the data for specific countries
Wave_6 <- WV6_Data_R_v20201117[WV6_Data_R_v20201117$C_COW_ALPHA %in% desired_countries, ]

```
# List of specific countries

Take only specific columns after we extracted only the desired countries. 7 Wave
```{r}

Wave_7_selected <- subset(Wave_7, select = c("C_COW_ALPHA", "Q46",
                                                                "Q47", "Q48", "Q49",
                                             "Q50", "Q57", "Q209", "Q210", "Q211", "Q212",
                                             "Q213",
                                             "Q215", "Q218", "Q219", "Q220", "Q172",
                                             "Q262", "Q260", "Q279"))

```

Take only specific columns after we extracted only the desired countries. 6 Wave
```{r cars}

Wave_6_selected <- subset(Wave_6, select = c("C_COW_ALPHA", "V10", "V11", "V55", "V23",
                                             "V59", "V24", "V85", "V86", "V87", "V88",
                                             "V146","V242", "V240", "V229"))

```

naming the attributes with meaningful names. 7 Wave
```{r}
library(dplyr)
Wave_7_renamed <- Wave_7_selected %>%
   rename(happiness = Q46, free_choice = Q48, health = Q47, life_satis = Q49,
          financial_satis = Q50, gen_trust = Q57,
          sign_pet = Q209, join_boycott = Q210,
          attend_demo = Q211, join_strike = Q212, donate = Q213, enc_poli = Q215, 
          sign_pet_onli = Q218, enc_poli_onli = Q219, org_poli_onli = Q220,
          religiosity = Q172, age = Q262, gender = Q260, employment = Q279, 
          country = C_COW_ALPHA)
          
```

naming the attributes with meaningful names. 6 Wave
```{r}
library(dplyr)
Wave_6_renamed <- Wave_6_selected %>%
   rename(happiness = V10, health = V11, free_choice = V55, life_satis = V23, 
          financial_satis = V59, gen_trust = V24, sign_pet = V85, join_boycott = V86,
          attend_demo = V87,
          join_strike = V88, religiosity = V146, age = V242, gender = V240,
          employment = V229, country = C_COW_ALPHA)
          
```

cleaning the dataset. 7 Wave
```{r}
for (col in names(Wave_7_renamed)) {
  Wave_7_renamed[[col]][Wave_7_renamed[[col]] %in% 
  c(-1, -2, -4, -5)] <- NA
}

```

cleaning the dataset. 6 Wave
```{r}
for (col in names(Wave_6_renamed)) {
  Wave_6_renamed[[col]][Wave_6_renamed[[col]] %in% 
  c(-1, -2, -4, -5)] <- NA
}
```

merge the two data sets.
```{r}
library(dplyr)
merged_data <- bind_rows(Wave_6_renamed, Wave_7_renamed)
merged_data <- merged_data[, !(names(merged_data) %in% c("org_poli_onli", "enc_poli_onli"
                                                         , "sign_pet_onli", "donate",
                                                         "enc_poli"))]
```

visualize the missing values for every attibute in the merged data.
```{r}
library(ggplot2)

# Assuming 'merged_data' is your data frame
missing_proportions <- colMeans(is.na(merged_data))
missing_data_df <- data.frame(variable = names(missing_proportions), proportion = missing_proportions)

# Create a bar chart to visualize missing data proportions
ggplot(missing_data_df, aes(x = variable, y = proportion)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  labs(title = "Proportion of Missing Data by Variable", x = "Variable", y = "Proportion Missing") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

specifying the location of the missing values within the attributes in the merged data.
``` {r}
library(naniar)
library(ggplot2)

# Function to summarize and visualize missing data for each country
missing_summary_and_visualization_by_country <- function(merged_data) {
  country <- unique(merged_data$country)[1]
  missing_summary <- sapply(merged_data, function(x) sum(is.na(x)))
  print(paste("Missing data summary for", country, ":"))
  print(missing_summary)
  
  plot <- naniar::vis_miss(merged_data) + 
    ggtitle(paste("Missing Data Visualization for", country)) +
    theme_minimal() +
    theme(plot.margin = margin(t = 0.5, r = 0.5, b = 2, l = 0.5, unit = "cm"),
          axis.text.x = element_text(angle = 90, hjust = 1))  # Adjust angle and bottom margin
  
  print(plot)
}

# Apply the function to each subset of the data, grouped by country
by(merged_data, merged_data$country, missing_summary_and_visualization_by_country)

```

calculating and printing the propotions of the missing data in the merged data.
```{r}
library(dplyr)
library(tidyr)
merged_data %>%
  group_by(country) %>%
  summarise(across(
    .cols = everything(),
    .fns = ~ mean(is.na(.x)),
    .names = "{.col}_missing_proportion"
  )) -> missing_proportions


# Print the result
print(missing_proportions)
```

visualize the missing data according to the attributes in merged data using dlookr library.
```{r}
library(dlookr)
plot_na_pareto(merged_data)
plot_na_intersect(merged_data)
```

a heat map for the miising data in the merged data.
```{r}
library(naniar)
gg_miss_fct(x = merged_data, fct = country)
```

creating a data frame to do iterations and imputation then do the missForest imputation method to handle the missing data.
```{r}
library(missRanger)
library(ggplot2)

merged_data_na <- data.frame(merged_data)

merged_imputet <- missRanger(
  merged_data_na, 
  formula = . ~ . ,
  num.trees = 1000, 
  verbose = 2, 
  seed = 111,  
  returnOOB = T)
```

calculating and printing the propotions of the missing data in the merged data after the imputation.
```{r}
library(dplyr)
library(tidyr)
merged_imputet_rounded %>%
  group_by(country) %>%
  summarise(across(
    .cols = everything(),
    .fns = ~ mean(is.na(.x)),
    .names = "{.col}_missing_proportion"
  )) -> missing_proportions_imputed

# Print the result
print(missing_proportions_imputed)
```

comparison between the imputed and the original data for *all attributes* by bar chart. *imputed in red*.
```{r}
library(ggplot2)
library(scales)

# Create the plot
data_columns <- setdiff(names(merged_data), c("country", "age", "gender"))


# Create a list to store plots
plots <- list()

# Generate bar charts for each column
for (col in data_columns) {
  unique_values <- unique(merged_data[[col]])
  plot <- ggplot() +
    geom_bar(data = merged_data, aes(x = factor(.data[[col]])), width = 0.3) +
    geom_bar(data = merged_imputet_rounded, aes(x = factor(.data[[col]])), fill = "red",
             position = position_nudge(x = 0.25), width = 0.3) +
    scale_x_discrete(breaks = unique_values, labels = numeric_labels[match(unique_values, merged_data[[col]])]) +
    labs(title = paste("Bar Chart for", col)) +
    theme_minimal()
  
  plots[[col]] <- plot
}

# Print or display the generated plots
for (col in data_columns) {
  print(plots[[col]])
}

```


comparison between the imputed and the original data for *religiosity* by bar chart. *imputed in red*.
```{r}
library(ggplot2)
library(scales)

# Define the string labels and their corresponding numeric values
numeric_labels <- c("1" = "Several times a day", "2"  = "Once a day",
                    "3" = "Several times each week",
                    "4" = "Only when attending religious services",
                    "5" = "Only on special holy days", "6" = "Once a year",
                    "7" = "Less often", "8" = "Never, practically never",
                    "null" = "null")

# Create the plot
ggplot() +
  geom_bar(data = merged_data, aes(x = factor(religiosity)), width = 0.3) +
  geom_bar(data = merged_imputet_rounded, aes(x = factor(religiosity)), fill = "red",
           position = position_nudge(x = 0.25), width = 0.3) +
  scale_x_discrete(breaks = unique(merged_data$religiosity), 
                   labels = numeric_labels) +  # Apply labels
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate and adjust

```

comparison between the imputed and the original data for *happiness* by bar chart. *imputed in red*.
```{r}
library(ggplot2)
library(scales)

# Define the string labels and their corresponding numeric values
numeric_labels <- c("1" = "Very happy", "2"  = "Quite happy", "3" = "Not very happy",
                    "4" = "Not at all happy", "null" = "null")

# Create the plot
ggplot() +
  geom_bar(data = merged_data, aes(x = factor(happiness)), width = 0.3) +
  geom_bar(data = merged_imputet_rounded, aes(x = factor(happiness)), fill = "red",
           position = position_nudge(x = 0.25), width = 0.3) +
  scale_x_discrete(breaks = unique(merged_data$happiness), 
                   labels = numeric_labels) +  # Apply labels
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate and adjust

```

comparison between the imputed and the original data for *free_choice* by bar chart. *imputed in red*.
```{r}
library(ggplot2)
library(scales)

# Define the string labels and their corresponding numeric values
numeric_labels <- c("1" = "None at all", "2" = "2", "3" = "3", "4" = "4", "5" = "5",
                    "6" = "6", "7" = "7", "8" = "8", "9" = "9",
                    "10" = "A great deal", "null" = "null ")

# Create the plot
ggplot() +
  geom_bar(data = merged_data, aes(x = factor(free_choice)), width = 0.3) +
  geom_bar(data = merged_imputet_rounded, aes(x = factor(free_choice)), fill = "red",
           position = position_nudge(x = 0.25), width = 0.3) +
  scale_x_discrete(breaks = unique(merged_data$free_choice), 
                   labels = numeric_labels) +  # Apply labels
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate and adjust

```

comparison between the imputed and the original data for *health* by bar chart. *imputed in red*.
```{r}
library(ggplot2)
library(scales)

# Define the string labels and their corresponding numeric values
numeric_labels <- c("1" = "Very good", "2" = "Good", "3" = "Fair",
                    "4" = "Poor", "5" = "Very poor", "null" = "null ")

# Create the plot
data_columns <- setdiff(names(merged_data), c("country", "age", "gender"))
ggplot() +
  geom_bar(data = merged_data, aes(x = factor(health)), width = 0.3) +
  geom_bar(data = merged_imputet_rounded, aes(x = factor(health)), fill = "red",
           position = position_nudge(x = 0.25), width = 0.3) +
  scale_x_discrete(breaks = unique(merged_data$health), 
                   labels = numeric_labels) +  # Apply labels
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate and adjust

```

comparison between the imputed and the original data for *life_satis* by bar chart. *imputed in red*.
```{r}
library(ggplot2)
library(scales)

# Define the string labels and their corresponding numeric values
numeric_labels <- c("1" = "Completely dissatisfied", "2" = "2", "3" = "3",
                    "4" = "4", "5" = "5", "6" = "6", "7" = "7", "8" = "8",
                    "9" = "9","10" = "Completely satisfied", "null" = "null")

# Create the plot
data_columns <- setdiff(names(merged_data), c("country", "age", "gender"))
ggplot() +
  geom_bar(data = merged_data, aes(x = factor(life_satis)), width = 0.3) +
  geom_bar(data = merged_imputet_rounded, aes(x = factor(life_satis)), fill = "red",
           position = position_nudge(x = 0.25), width = 0.3) +
  scale_x_discrete(breaks = unique(merged_data$life_satis), 
                   labels = numeric_labels) +  # Apply labels
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate and adjust

```

comparison between the imputed and the original data for *financial_satis* by bar chart. *imputed in red*.
```{r}
library(ggplot2)
library(scales)

# Define the string labels and their corresponding numeric values
numeric_labels <- c("1" = "dissatisfied", "2" = "2", "3" = "3",
                    "4" = "4", "5" = "5", "6" = "6", "7" = "7", "8" = "8",
                    "9" = "9","10" = "satisfied", "null" = "null")

# Create the plot
data_columns <- setdiff(names(merged_data), c("country", "age", "gender"))
ggplot() +
  geom_bar(data = merged_data, aes(x = factor(financial_satis)), width = 0.3) +
  geom_bar(data = merged_imputet_rounded, aes(x = factor(financial_satis)), fill = "red",
           position = position_nudge(x = 0.25), width = 0.3) +
  scale_x_discrete(breaks = unique(merged_data$financial_satis), 
                   labels = numeric_labels) +  # Apply labels
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate and adjust

```

comparison between the imputed and the original data for *gen_trust* by bar chart. *imputed in red*.
```{r}
library(ggplot2)
library(scales)

# Define the string labels and their corresponding numeric values
numeric_labels <- c("1" = "Most people can be trusted", "2" = "Need to be very careful",
                    "null" = "null ")

# Create the plot
data_columns <- setdiff(names(merged_data), c("country", "age", "gender"))
ggplot() +
  geom_bar(data = merged_data, aes(x = factor(gen_trust)), width = 0.3) +
  geom_bar(data = merged_imputet_rounded, aes(x = factor(gen_trust)), fill = "red",
           position = position_nudge(x = 0.25), width = 0.3) +
  scale_x_discrete(breaks = unique(merged_data$gen_trust), 
                   labels = numeric_labels) +  # Apply labels
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate and adjust

```

comparison between the imputed and the original data for *sign_pet* by bar chart. *imputed in red*.
```{r}
library(ggplot2)
library(scales)

# Define the string labels and their corresponding numeric values
numeric_labels <- c("1" = "Have done", "2" = "Might do",
                    "3" = "Would never do", "null" = "null ")

# Create the plot
data_columns <- setdiff(names(merged_data), c("country", "age", "gender"))
ggplot() +
  geom_bar(data = merged_data, aes(x = factor(sign_pet)), width = 0.3) +
  geom_bar(data = merged_imputet_rounded, aes(x = factor(sign_pet)), fill = "red",
           position = position_nudge(x = 0.25), width = 0.3) +
  scale_x_discrete(breaks = unique(merged_data$sign_pet), 
                   labels = numeric_labels) +  # Apply labels
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate and adjust

```

comparison between the imputed and the original data for *join_boycott* by bar chart. *imputed in red*.
```{r}
library(ggplot2)
library(scales)

# Define the string labels and their corresponding numeric values
numeric_labels <- c("1" = "Have done", "2" = "Might do",
                    "3" = "Would never do", "null" = "null ")

# Create the plot
data_columns <- setdiff(names(merged_data), c("country", "age", "gender"))
ggplot() +
  geom_bar(data = merged_data, aes(x = factor(join_boycott)), width = 0.3) +
  geom_bar(data = merged_imputet_rounded, aes(x = factor(join_boycott)), fill = "red",
           position = position_nudge(x = 0.25), width = 0.3) +
  scale_x_discrete(breaks = unique(merged_data$join_boycott), 
                   labels = numeric_labels) +  # Apply labels
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate and adjust

```

comparison between the imputed and the original data for *attend_demo* by bar chart. *imputed in red*.
```{r}
library(ggplot2)
library(scales)

# Define the string labels and their corresponding numeric values
numeric_labels <- c("1" = "Have done", "2" = "Might do",
                    "3" = "Would never do", "null" = "null ")

# Create the plot
data_columns <- setdiff(names(merged_data), c("country", "age", "gender"))
ggplot() +
  geom_bar(data = merged_data, aes(x = factor(attend_demo)), width = 0.3) +
  geom_bar(data = merged_imputet_rounded, aes(x = factor(attend_demo)), fill = "red",
           position = position_nudge(x = 0.25), width = 0.3) +
  scale_x_discrete(breaks = unique(merged_data$attend_demo), 
                   labels = numeric_labels) +  # Apply labels
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate and adjust

```

comparison between the imputed and the original data for *join_strike* by bar chart. *imputed in red*.
```{r}
library(ggplot2)
library(scales)

# Define the string labels and their corresponding numeric values
numeric_labels <- c("1" = "Have done", "2" = "Might do",
                    "3" = "Would never do", "null" = "null ")

# Create the plot
data_columns <- setdiff(names(merged_data), c("country", "age", "gender"))
ggplot() +
  geom_bar(data = merged_data, aes(x = factor(join_strike)), width = 0.3) +
  geom_bar(data = merged_imputet_rounded, aes(x = factor(join_strike)), fill = "red",
           position = position_nudge(x = 0.25), width = 0.3) +
  scale_x_discrete(breaks = unique(merged_data$join_strike), 
                   labels = numeric_labels) +  # Apply labels
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate and adjust

```

comparison between the imputed and the original data for *employment* by bar chart. *imputed in red*.
```{r}
library(ggplot2)
library(scales)

# Define the string labels and their corresponding numeric values
numeric_labels <- c("1" = "Full time", "2" = "Part time", "3" = "Self employed",
                    "4" = "Retired", "5" = "Housewife not otherwise employed",
                    "6" = "Student", "7" = "Unemployed", "8" = "Other",
                    "null" = "null")

# Create the plot
data_columns <- setdiff(names(merged_data), c("country", "age", "gender"))
ggplot() +
  geom_bar(data = merged_data, aes(x = factor(employment)), width = 0.3) +
  geom_bar(data = merged_imputet_rounded, aes(x = factor(employment)), fill = "red",
           position = position_nudge(x = 0.25), width = 0.3) +
  scale_x_discrete(breaks = unique(merged_data$employment), 
                   labels = numeric_labels) +  # Apply labels
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate and adjust

```

renaming the data in the data set.
```{r}
#=======employment==========================================================================
employment_mapping <- c(
  "1" = "Full time",
  "2" = "Part time",
  "3" = "Self employed",
  "4" = "Retired",
  "5" = "Housewife not otherwise employed",
  "6" = "Student",
  "7" = "Unemployed",
  "8" = "Other",
  "null" = "null"
)
#=======join_strike=========================================================================

join_strike_mapping <- c(
  "1" = "Have done",
  "2" = "Might do",
  "3" = "Would never do",
  "null" = "null"
)
#=======attend_demo=========================================================================

attend_demo_mapping <- c(
  "1" = "Have done",
  "2" = "Might do",
  "3" = "Would never do",
  "null" = "null"
)
#=======join_boycott========================================================================

join_boycott_mapping <- c(
  "1" = "Have done",
  "2" = "Might do",
  "3" = "Would never do",
  "null" = "null"
)
#=======sign_pet============================================================================

sign_pet_mapping <- c(
  "1" = "Have done",
  "2" = "Might do",
  "3" = "Would never do",
  "null" = "null"
)
#=======gen_trust===========================================================================

gen_trust_mapping <- c(
  "1" = "Most people can be trusted",
  "2" = "Need to be very careful",
  "null" = "null"
)
#=======financial_satis=====================================================================

financial_satis_mapping <- c(
  "1" = "Dissatisfied",
  "2" = "2",
  "3" = "3",
  "4" = "4",
  "5" = "5",
  "6" = "6",
  "7" = "7",
  "8" = "8",
  "9" = "9",
  "10" = "Satisfied",
  "null" = "null"
)
#=======life_satis==========================================================================

life_satis_mapping <- c(
  "1" = "compeltely dissatisfied",
  "2" = "2",
  "3" = "3",
  "4" = "4",
  "5" = "5",
  "6" = "6",
  "7" = "7",
  "8" = "8",
  "9" = "9",
  "10" = "compeltely Satisfied",
  "null" = "null"
)
#=======health============================================================================

health_mapping <- c(
  "1" = "Very good",
  "2" = "Good",
  "3" = "Fair",
  "4" = "Poor",
  "5" = "Very poor",
  "null" = "null"
)
#=======free_choice=========================================================================

free_choice_mapping <- c(
  "1" = "None at all",
  "2" = "2",
  "3" = "3",
  "4" = "4",
  "5" = "5",
  "6" = "6",
  "7" = "7",
  "8" = "8",
  "9" = "9",
  "10" = "A great deal",
  "null" = "null"
)
#=======happiness===========================================================================

happiness_mapping <- c(
  "1" = "Very happy",
  "2" = "Quite happy",
  "3" = "Not very happy",
  "4" = "Not at all happy",
  "null" = "null"
)
#=======gender===========================================================================

gender_mapping <- c(
  "1" = "Male",
  "2" = "Female",
  "null" = "null"
)

#=======religiosity=========================================================================

religiosity_mapping <- c(
  "1" = "Several times a day",
  "2"  = "Once a day",
  "3" = "Several times each week",
  "4" = "Only when attending religious services",
  "5" = "Only on special holy days",
  "6" = "Once a year",
  "7" = "Less often",
  "8" = "Never, practically never",
  "null" = "null"
)

#=======adding changes to new data frame====================================================

merged_renamed <- merged_imputet_rounded %>%
  mutate(
    employment = employment_mapping[as.character(employment)],
    join_strike = join_strike_mapping[as.character(join_strike)],
    attend_demo = attend_demo_mapping[as.character(attend_demo)],
    join_boycott = join_boycott_mapping[as.character(join_boycott)],
    sign_pet = sign_pet_mapping[as.character(sign_pet)],
    gen_trust = gen_trust_mapping[as.character(gen_trust)],
    financial_satis = financial_satis_mapping[as.character(financial_satis)],
    life_satis = life_satis_mapping[as.character(life_satis)],
    health = health_mapping[as.character(health)],
    free_choice = free_choice_mapping[as.character(free_choice)],
    happiness = happiness_mapping[as.character(happiness)],
    gender = gender_mapping[as.character(gender)],
    religiosity = religiosity_mapping[as.character(religiosity)]
  )
# Print the new dataframe
print(merged_renamed)
```

calculating the descriptive statistics for the whole data.
```{r}

library(e1071)

descriptive_summary <- function(data, variables) {
  summaries <- list() # Initialize a list to store the summaries
  
  for (variable_name in variables) {
    variable <- data[[variable_name]]
    summary_list <- data.frame(
      variable_name = variable_name,
      mean = mean(variable, na.rm = TRUE),
      median = median(variable, na.rm = TRUE),
      mode = as.numeric(names(sort(table(variable), decreasing = TRUE)[1])),
      variance = var(variable, na.rm = TRUE),
      standard_deviation = sd(variable, na.rm = TRUE),
      range = paste(range(variable, na.rm = TRUE), collapse = " - "),
      iqr = IQR(variable, na.rm = TRUE),
      skewness = skewness(variable, na.rm = TRUE),
      kurtosis = kurtosis(variable, na.rm = TRUE)
    )
    
    summaries[[variable_name]] <- summary_list # Add the summary list to the summaries list
  }
  
  # Combine the summaries into a single data frame
  summary_data <- do.call(rbind, summaries)
  
  return(summary_data)
}

variables <- c("happiness", "gen_trust", "health", "free_choice",
               "life_satis", "financial_satis", "gen_trust",
               "sign_pet", "join_boycott", "attend_demo",
               "join_strike", "religiosity", 
               "age", "gender", "employment") 

# Example Usage
variable_summary <- descriptive_summary(merged_imputet_rounded, variables)
print(variable_summary)
```

calculating the descriptive data for each country and put it in a list of data frames.
```{r}
library(e1071)
library(dplyr)

descriptive_summary <- function(data, variables) {
  country_summaries <- list() # Initialize a list to store country summaries
  
  for (country_name in unique(data$country)) {
    country_data <- data %>%
      filter(country == country_name)
    
    country_summary <- list()
    
    for (variable_name in variables) {
      variable_summary <- country_data %>%
        summarize(
          variable_name = variable_name,
          mean = mean(!!sym(variable_name), na.rm = TRUE),
          median = median(!!sym(variable_name), na.rm = TRUE),
          mode = as.numeric(names(sort(table(!!sym(variable_name)), decreasing = TRUE)[1])),
          variance = var(!!sym(variable_name), na.rm = TRUE),
          standard_deviation = sd(!!sym(variable_name), na.rm = TRUE),
          range = paste(range(!!sym(variable_name), na.rm = TRUE), collapse = " - "),
          iqr = IQR(!!sym(variable_name), na.rm = TRUE),
          skewness = skewness(!!sym(variable_name), na.rm = TRUE),
          kurtosis = kurtosis(!!sym(variable_name), na.rm = TRUE)
        )
      
      country_summary[[variable_name]] <- variable_summary
    }
    
    country_summaries[[country_name]] <- country_summary
  }
  
  return(country_summaries)
}

variables <- c("happiness", "gen_trust", "health", "free_choice",
               "life_satis", "financial_satis", "gen_trust",
               "sign_pet", "join_boycott", "attend_demo",
               "join_strike", "religiosity", 
               "age", "gender", "employment") 

# Example Usage
country_variable_summaries <- descriptive_summary(merged_imputet_rounded, variables)

# Print summaries for a specific country and variable
print(country_variable_summaries$CountryName$variable_name)

```

calculate the values separately and visualize it.
```{r}
# Load required libraries
library(dplyr)
library(moments)
library(ggplot2)

# Assuming your dataset is named "your_dataset"
# Replace "your_dataset" with the actual name of your dataset

country_data <- merged_imputet_rounded %>%
  filter(country == "EGY")  # Filter data for EGY country

# List of variable names to calculate statistics for
variable_names <- c("happiness", "gen_trust", "health", "free_choice",
                    "life_satis", "financial_satis", "gen_trust",
                    "sign_pet", "join_boycott", "attend_demo",
                    "join_strike", "religiosity", 
                    "age", "gender", "employment")

# Initialize an empty list to store results
results_list <- list()

# Loop through each variable and calculate statistics
for (variable_name in variable_names) {
  variable_stats <- country_data %>%
    summarise(
      variable_name = variable_name,
      mean = mean(!!sym(variable_name), na.rm = TRUE),
      median = median(!!sym(variable_name), na.rm = TRUE),
      mode = as.numeric(names(sort(table(!!sym(variable_name)), decreasing = TRUE)[1])),
      variance = var(!!sym(variable_name), na.rm = TRUE),
      standard_deviation = sd(!!sym(variable_name), na.rm = TRUE),
      range = paste(range(!!sym(variable_name), na.rm = TRUE), collapse = " - "),
      iqr = IQR(!!sym(variable_name), na.rm = TRUE),
      skewness = skewness(!!sym(variable_name), na.rm = TRUE),
      kurtosis = kurtosis(!!sym(variable_name), na.rm = TRUE)
    )
  
  results_list[[variable_name]] <- variable_stats
}

# Combine results into a single data frame
results_df <- bind_rows(results_list)

# Print the results
print(results_df)


# List of variables to exclude
excluded_variables <- c("age", "gender")

# Filter out the excluded variables from the dataframe
filtered_results <- results_df %>% filter(!variable_name %in% excluded_variables)

# Create a bar chart for mean values
mean_bar_chart <- ggplot(filtered_results, aes(x = variable_name, y = mean)) +
  geom_bar(stat = "identity", fill = "blue") +
  labs(title = "Mean Values for Different Variables (Excluding Age and Gender) in EGY Country",
       x = "Variable", y = "Mean Value") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Print the bar chart
print(mean_bar_chart)

```

```{r}
library(writexl)


# Initialize an empty list to store data frames
summary_data_frames <- list()

# Loop through each country
for (country_name in names(country_variable_summaries)) {
  country_data <- country_variable_summaries[[country_name]]
  
  # Convert the nested list of summary statistics to a data frame
  country_df <- do.call(rbind, country_data)
  
  # Add a new column for the country name
  country_df$CountryName <- country_name
  
  # Append the data frame to the list
  summary_data_frames[[country_name]] <- country_df
}

# Combine data frames from different countries into one data frame
combined_summary_df <- do.call(rbind, summary_data_frames)

# Specify the path and file name for the Excel file
excel_file_path <- "C:/Users/LENOVO/Desktop/DataMohammed/Data/summary_statistics.xlsx"

# Export the combined data frame to an Excel file
write_xlsx(combined_summary_df, path = excel_file_path)

```