---
title: "Data"
author: "masri"
date: "2023-08-06"
output: html_document
---

A code chunk only for libraries.
```{r}
library(dplyr)
library(poliscidata)

```

taking only the 7 desired countries from the original dataset. 7 Wave
```{r}
desired_countries <- c("JOR", "IRQ", "TUN", "MOR", "EGY", "LBN", "LBY")

# Filter the data for specific countries
Wave_7 <- Wave_7[Wave_7$B_COUNTRY_ALPHA %in% desired_countries, ]

```

taking only the 7 desired countries from the original dataset. 6 Wave
```{r}
desired_countries <- c("JOR", "IRQ", "TUN", "MOR", "EGY", "LBN", "LBY")

# Filter the data for specific countries
Wave_6 <- Wave_6[Wave_6$B_COUNTRY_ALPHA %in% desired_countries, ]

```
# List of specific countries

Take only specific columns after we extracted only the desired countries. 7 Wave
```{r}

Wave_7_selected <- subset(Wave_7, select = c("B_COUNTRY_ALPHA", "Q46", "Q47", "Q48", "Q49",
                                             "Q50", "Q57","Q65", "Q68", "Q70", "Q71", "Q72",
                                             "Q73","Q209", "Q210", "Q211", "Q212", "Q213",
                                             "Q215", "Q218", "Q219", "Q220", "Q173",
                                             "Q262", "Q260", "Q279"))

```

Take only specific columns after we extracted only the desired countries. 6 Wave

```{r cars}

Wave_6_selected <- subset(Wave_6, select = c("B_COUNTRY_ALPHA", "V10", "V11", "V55", "V23",
                                             "V59", "V24","V109", "V112", "V114", "V115",
                                             "V116","V117", "V85", "V86", "V87", "V88",
                                             "V147","V242", "V240", "V229"))

```


naming the attributes with meaningful names. 7 Wave

```{r}

Wave_7_renamed <- Wave_7_selected %>%
   rename(happiness = Q46, free_choice = Q48, health = Q47, life_satis = Q49,
          financial_satis = Q50, gen_trust = Q57,
          armed_trust = Q65, labor_trust = Q68, court_trust = Q70, gov_trust = Q71, 
          parties_trust = Q72, Parliament_trust = Q73, sign_pet = Q209, join_boycott = Q210,
          attend_demo = Q211, join_strike = Q212, donate = Q213, enc_poli = Q215, 
          sign_pet_onli = Q218, enc_poli_onli = Q219, org_poli_onli = Q220,
          religiosity = Q173, age = Q262, gender = Q260, employment = Q279, 
          country = B_COUNTRY_ALPHA)
          
```

naming the attributes with meaningful names. 6 Wave

```{r}

Wave_6_renamed <- Wave_6_selected %>%
   rename(happiness = V10, health = V11, free_choice = V55, life_satis = V23, 
          financial_satis = V59, gen_trust = V24, armed_trust = V109, 
          labor_trust = V112, court_trust = V114, gov_trust = V115, parties_trust = V116,
          Parliament_trust = V117, sign_pet = V85, join_boycott = V86, attend_demo = V87,
          join_strike = V88, religiosity = V147, age = V242, gender = V240,
          e0mployment = V229, country = B_COUNTRY_ALPHA)
          
```

cleaning the dataset. 7 Wave
```{r}
for (col in names(Wave_7_renamed)) {
  Wave_7_renamed[[col]][Wave_7_renamed[[col]] %in% 
  c(-1, -2, -4, -5)] <- NA
}

```

cleaning the dataset. 6 Wave
```{r}
for (col in names(Wave_6_renamed)) {
  Wave_6_renamed[[col]][Wave_6_renamed[[col]] %in% 
  c(-1, -2, -4, -5)] <- NA
}
```
